Advancements in Moltres for Time-Dependent Multiphysics Molten Salt Reactor Modeling

### 2024-11-13 hybrid.tex
Full draft + edits

Consequently, most of this chapter focuses on the $S_N$ and the drift correction-based hybrid
method implementations on Moltres. On the other hand, I implemented the diffusion correction-based
hybrid method using the Python programming language for quick
prototyping. Implementation details of the $S_N$, neutron diffusion, and hybrid methods on Python
are available in Appendix \ref{chap:implementation}. Both correction schemes share the iteration
algorithm described in Section \ref{sec:hybrid-algorithm}.

@@

Here, I use Case 3b of the 1-D test cases to be covered in Chapter \ref{chap:msre}
to illustrate the buffer region and the behavior of $\vec{D}_g$. Case 3b is a 1-D slab problem
consisting of control rod, air, fuel-graphite repeating lattice, and reactor vessel regions as
shown in Figure \ref{fig:3b-geometry}. The fuel regions are neutron-multiplying media containing
$^\text{235}$U fissile material. I took material compositions of each region from the \gls{MSRE}
reference design and the start-up fuel composition \cite{fratoni_molten_2020}.
Case 3b has reflecting boundary conditions on the left boundary and vacuum boundary conditions on
the right boundary.
%
\begin{figure}[htb!]
    \centering
    \begin{subfigure}[t]{.49\textwidth}
        \centering
        \includegraphics[width=\textwidth]{case-3b-group-1-drift}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{.49\textwidth}
        \centering
        \includegraphics[width=\textwidth]{case-3b-group-8-drift}
    \end{subfigure}
    \caption{The reference and hybrid drift ($\vec{D}_g$) distributions for group 1 and 8 calculated
      from $S_8$ and $S_8$-diffusion simulations. The correction subregion $V_1$ spans $x=0$ cm to
      $x=10$ cm.}
    \label{fig:3b-drift}
\end{figure}

I ran an eight energy group $S_8$ $k$-eigenvalue simulation with the newly implemented $S_N$ solver
on Moltres to generate reference $\vec{D}_g$ distributions. I also ran an eight-group hybrid
$S_8$-diffusion simulation with the $S_8$ method for generating $\vec{D}_g$ in $V_1$. I set $V_1$
to encompass the control rod region and its vicinity from $x=0$ to $10$ cm based on the geometry in
Figure \ref{fig:3b-geometry}. Figure \ref{fig:3b-drift} shows the $\vec{D}_1$ and $\vec{D}_8$
distributions from $x=0$ to $15$ from the reference $S_8$ and hybrid simulations. The hybrid
$\vec{D}_g$ distribution is zero beyond $x=10$ cm because no corrections are generated outside of
$V_1$. Comparing the hybrid distributions to the reference distributions in both energy groups, the
hybrid distributions are accurate up to around $x=8$ cm. Working backward towards the control rod
at $x=0$-$0.5$ cm, the $\vec{D}_g$ values go to zero at $x=7.5$ cm. Therefore, the buffer
region $V_1'$ lies between $x=7.5$ cm and $x=10$ cm. While $V_1$ is pre-determined at the start of
the simulation and fixed for all energy groups, $V_1'$ does not necessarily coincide for all
energy groups and coordinate axes.

>>>>

Consequently, most of this chapter focuses on the $S_N$ and the drift correction-based hybrid
method implementations on Moltres. On the other hand, I implemented the diffusion correction-based
hybrid method using the Python programming language for quick
prototyping. Implementation details of the $S_N$, neutron diffusion, and hybrid methods in Python
are available in Appendix \ref{chap:implementation}. Both correction schemes share the iteration
algorithm described in Section \ref{sec:hybrid-algorithm}.

@@

Here, I use Case 3b of the 1-D test cases to be covered in Chapter \ref{chap:msre}
to illustrate the buffer region and the behavior of $\vec{D}_g$. Case 3b is a 1-D slab problem
consisting of control rod, air, fuel-graphite repeating lattice, and reactor vessel regions as
shown in Figure \ref{fig:3b-geometry}. The fuel regions are neutron-multiplying media containing
$^\text{235}$U fissile material. I took material compositions of each region from the \gls{MSRE}
reference design and the start-up fuel composition \cite{fratoni_molten_2020}.
Case 3b has reflecting boundary conditions on the left boundary and vacuum boundary conditions on
the right boundary.
%
\begin{figure}[htb!]
    \centering
    \begin{subfigure}[t]{.49\textwidth}
        \centering
        \includegraphics[width=\textwidth]{case-3b-group-1-drift}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{.49\textwidth}
        \centering
        \includegraphics[width=\textwidth]{case-3b-group-8-drift}
    \end{subfigure}
    \caption{The reference and hybrid drift ($\vec{D}_g$) distributions for group 1 and 8 calculated
      from $S_8$ and $S_8$-diffusion simulations. The correction subregion $V_1$ spans $x=0$ cm to
      $x=10$ cm.}
    \label{fig:3b-drift-1}
\end{figure}

I ran an eight energy group $S_8$ $k$-eigenvalue simulation with the newly implemented $S_N$ solver
on Moltres to generate reference $\vec{D}_g$ distributions. I also ran an eight-group hybrid
$S_8$-diffusion simulation with the $S_8$ method for generating $\vec{D}_g$ in $V_1$. I set $V_1$
to encompass the control rod region and its vicinity from $x=0$ to $10$ cm based on the geometry in
Figure \ref{fig:3b-geometry}. Figure \ref{fig:3b-drift-1} shows the $\vec{D}_1$ and $\vec{D}_8$
distributions from $x=0$ to $15$ from the reference $S_8$ and hybrid simulations. The hybrid
$\vec{D}_g$ distribution is zero beyond $x=10$ cm because no corrections are generated outside of
$V_1$. Comparing the hybrid distributions to the reference distributions in both energy groups, the
hybrid distributions are accurate up to around $x=8$ cm. Working backward towards the control rod
at $x=0$-$0.5$ cm, the $\vec{D}_g$ values go to zero at $x=7.5$ cm. Therefore, the buffer
region $V_1'$ lies between $x=7.5$ cm and $x=10$ cm. While $V_1$ is pre-determined at the start of
the simulation and fixed for all energy groups, $V_1'$ does not necessarily coincide for all
energy groups and coordinate axes.

### 2024-11-13 main.tex
saaf sn method
add verification chapter for referencing, hybrid chapter edits
Fix typos and add numerical implementation section
final edits for first draft of chapter 4; add image files for chapter 2,3,4
MSRE chapter edits
msre chapter edits
chapter 5 draft
turbulence verification section
Chapter 5 summary
Chapter 6 content
Full draft + edits

%% Package and Class "uiucthesis2021" for use with LaTeX2e.
\documentclass[edeposit,fullpage,11pt]{uiucthesis2021}
\doublespacing

@@

\usepackage{tabularx}
\usepackage{float}
\usepackage{enumitem}
\usepackage{diagbox}
\usepackage{courier}
\usepackage{pdflscape}

\usepackage{cleveref}
\usepackage{datatool}
\usepackage[numbers]{natbib}
\usepackage{notoccite}

@@

\title{A Hybrid Neutronics Method for Time-Dependent Control Rod Modeling in Molten Salt Reactors}
\author{Sun Myung Park}
\department{Nuclear, Plasma \& Radiological Engineering}
\prelim
\degreeyear{2024}
\committee{Dr Madicken Munk, Chair \\
           Professor Rizwan Uddin \\
           Associate Professor Tomasz Kozlowski \\
           Professor Paul Fischer}

@@

%\input{abstract}

@@

%\begin{acknowledgments}
%
%%\input{acks}
%
%\end{acknowledgments}
%\addcontentsline{toc}{chapter}{Acknowledgments}

@@

\chapter{Introduction}
\label{chap:intro}
%\input{introduction}
%\glsresetall

\chapter{Molten Salt Reactor Modeling and Simulation}
\label{chap:lit}
\input{lit}
\glsresetall
%
%\chapter{Description of Moltres and Assessment of its Current Capabilities}
%\label{chap:moltres}
%\input{moltres}
%\glsresetall
%
%\chapter{Verification of Moltres for Multiphysics Molten Salt
%Reactor Modeling}
%\label{chap:benchmark}
%\input{benchmark}
%\glsresetall
%
%\chapter{Hybrid S$_\text{N}$-Diffusion Method for Improved Control Rod Modeling
%in Neutron Diffusion Methods}
%\label{chap:hybrid}
%\input{hybrid}
%\glsresetall
%
%\chapter{Proposed Work}
%\label{chap:proposedwork}
%\input{proposed-work}
%\glsresetall

@@

\bibliographystyle{IEEEtran}
\bibliography{bibliography}

>>>>

%% Package and Class "uiucthesis2021" for use with LaTeX2e.
\documentclass[11pt]{uiucthesis2021}
\doublespacing

@@

\usepackage{tabularx}
\usepackage{float}
\usepackage{enumitem}
\setlist[itemize]{noitemsep}
\usepackage{diagbox}
\usepackage{courier}
\usepackage{pdflscape}

\usepackage{cleveref}
\usepackage{datatool}
% \usepackage[numbers]{natbib}
\usepackage{notoccite}

\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[bibstyle=ieee,backend=bibtex8,sorting=none,eprint=false,isbn=false,doi=false]{biblatex}
\usepackage{textalpha}
\addbibresource{./bibliography.bib}
\AtEveryBibitem{%
  \clearfield{note}%
}

@@

%\title{A Hybrid Neutronics Method for Time-Dependent Control Rod Modeling in Molten Salt Reactors}
\title{Advancements in Moltres for Time-Dependent Multiphysics Molten Salt Reactor Modeling}
\author{Sun Myung Park}
\department{Nuclear, Plasma \& Radiological Engineering}
\degreeyear{2024}
\committee{Associate Professor Kathryn D. Huff, Chair \& Co-Director of Research \\
           Assistant Professor Madicken Munk, Co-Director of Research, Oregon State University \\
           Professor Rizwan Uddin \\
           Professor Tomasz Kozlowski \\
           Professor Paul Fischer}

\newcounter{counterforappendices}

@@

\input{abstract}

@@

\begin{acknowledgments}

%\input{acks}

\end{acknowledgments}
\addcontentsline{toc}{chapter}{Acknowledgments}

@@

\chapter{Introduction}
\label{chap:intro}
\input{introduction}
\glsresetall

\chapter{Molten Salt Reactor Modeling and Simulation}
\label{chap:lit}
\input{lit}
\glsresetall

\chapter{Verification of Multiphysics Features in Moltres}
\label{chap:verification}
\input{verification}
\glsresetall

\chapter{Hybrid $S_N$-Diffusion Method}
\label{chap:hybrid}
\input{hybrid}
\glsresetall

\chapter{Demonstration of the Hybrid Method with the MSRE}
\label{chap:msre}
\input{msre}
\glsresetall

\chapter{Demonstration of Time-Dependent Reactivity-Initiated Transients}
\label{chap:transient}
\input{transient}
\glsresetall

\chapter{Conclusion}
\label{chap:conclusion}
\input{conclusion}
\glsresetall

@@

{
\setstretch{1}
% \bibliographystyle{IEEEtran}
\printbibliography[heading=bibintoc,title={References}]
}

\clearpage
\setcounter{counterforappendices}{\value{page}}
\mainmatter
\setcounter{page}{\value{counterforappendices}}
\appendix
\input{appendix}

### 2024-11-13 msre.tex
Full draft + edits

In Chapter \ref{chap:hybrid}, I laid out the mathematical background and numerical implementation
of the hybrid $S_N$-diffusion method for improving neutronic accuracy in reactor systems containing
highly neutron-absorbing regions. I developed and implemented the diffusion and drift correction
schemes for the hybrid method on Python and Moltres, respectively. This chapter demonstrates
the hybrid method through 1-D, 2-D, and 3-D $k$-eigenvalue simulations of the \gls{MSRE}.
I employed the OpenMC Monte Carlo neutral particle transport software \cite{romano_openmc:_2015} to
generate group constants for the hybrid method and reference solutions for method verification.
The 1-D models serve to verify the newly-implemented $S_N$ and hybrid methods
against OpenMC as well as to analyze the impact of key input parameters on the hybrid method. The
2-D models test the hybrid method performance through increased spatial dimensionality and reduced
geometric asymmetry relative to the 1-D models. Lastly, the 3-D models serve as neutronics model
validation against the \gls{MSRE} benchmark model by Fratoni et al.\ \cite{fratoni_molten_2020}, a
testbed for \gls{HPC} scaling tests, and preparation for the time-dependent multiphysics
simulations in Chapter \ref{chap:transient}.

@@

Group constants relevant to the neutron diffusion, $S_N$ neutron transport, or both
methods are:
%
\begin{itemize}
  \item $\Sigma_{t,g}$: Macroscopic total cross section in group $g$,
  \item $\Sigma_{r,g}$: Macroscopic removal cross section in group $g$,
  \item $\Sigma_s^{g'\rightarrow g}$: Macroscopic group-to-group scattering cross section matrix,
  \item $\Sigma_{s,l}^{g'\rightarrow g}$: $l$-th Legendre moment of the macroscopic
    group-to-group scattering cross section matrix,
  \item $\Sigma_{sp,l}^{g'\rightarrow g}$: $l$-th Legendre moment of the macroscopic
    group-to-group scattering production cross section matrix,
  \item $D_g$: $P_1$-based diffusion coefficient in group $g$,
  \item $\nu\Sigma_{f,g}$: Product of the average number of neutrons produced per fission and the
    macroscopic fission cross section in group $g$,
  \item $\chi_g$: Neutron fission spectrum in group $g$.
\end{itemize}
%
I generated the group constants using OpenMC's multigroup cross section generation capability
\cite{boyd_multigroup_2019}. A group constant postprocessing script for Moltres
(\texttt{moltres\_xs.py}) parses OpenMC simulation output files and rewrites the group constant
data into a JSON format file suitable for Moltres simulations. While OpenMC provides most of the
group constants directly, the postprocessing script calculates $\Sigma_{r,g}$ as
%
\begin{align}
  \Sigma_{r,g} =& \sum^G_{g'\neq g}\Sigma_s^{g\rightarrow g'}+\Sigma_{a,g}-\left(\Sigma_{sp}^{g
    \rightarrow g} - \Sigma_s^{g\rightarrow g}\right)
  \shortintertext{where}
      \Sigma_{a,g} =& \mbox{ macroscopic absorption cross section in group $g$,} \nonumber \\
      \Sigma_{sp}^{g\rightarrow g} =& \mbox{ macroscopic scattering production cross section from
      group $g$ to $g$.} \nonumber
\end{align}
%
$\Sigma_{r,g}$ primarily represents the loss of neutrons from group $g$ through outscattering and
absorption. $\Sigma_{sp}^{g\rightarrow g}$ incorporates neutron multiplication effects from neutron
knockout reactions into the scattering cross section. Neutronics codes commonly identify neutron
knockout reactions as scattering reactions, but $\Sigma_{r,g}$ is a convenient parameter in which
to incorporate neutron knockout effects in the neutron diffusion method. I ran all test cases
for $S_N$ and hybrid method calculations with scattering cross sections approximated by up to 2nd
Legendre moments ($L=2$).

@@

The rest of this section pertains to the deterministic neutronics methods used in this work for
modeling the \gls{MSRE}.
For the 1-D models, I performed neutronics calculations with the $S_N$, neutron diffusion, and
hybrid method implementations on Moltres and Python. Table \ref{table:nts-methods} highlights the
differences between the two implementations. The $S_N$ neutron transport method implementation on
Moltres follows the methodology for solving the \gls{SAAF} formulation of the $S_N$ equations as
described in Section \ref{sec:saaf} while the implementation on Python follows the methodology
for solving the original first-order formulation as described in Section \ref{sec:python-sn}.

The implementations on Moltres discretize the problem domain in space using the finite element
method while the implementations on Python use finite difference or diamond difference schemes. The
most crucial difference lies in the transport correction formulations for the hybrid method. The
Moltres implementation uses the drift correction scheme described in Section
\ref{sec:drift-correction} while the Python implementation uses the diffusion correction
scheme described in Section \ref{sec:diffusion-correction}.

@@

@@

@@

\begin{itemize}
  \item Ignored thermal expansion of all reactor components.
  \item Modeled the control rods as perfectly annular cylinders instead of beaded control elements
    strung on flexible steel cables. Ignored the inconel shells encasing the control elements and
    the steel helical cables linking the control elements together.
  \item Set channel pitch, width, and length to 2, 0.2, and 1.2 inches, respectively.
  \item Homogenized the INOR-8, graphite, and molten salt regions in the sample basket.
  \item Modified the outer edge of the core graphite to be circular with no jagged edges.
  \item Replaced partial channels with full-size channels near the edge of the core graphite.
  \item Ignored the thermal insulation and shield structures outside the core.
\end{itemize}

@@

@@

@@

\begin{table}[htb]
  \centering
  \caption{List of reactor dimensions.}
  \begin{tabular}{l l}
    \toprule
    Height [cm] & 215 \\
    \midrule
    TODO: Populate table & \\
    \bottomrule
  \end{tabular}
  \label{table:reactor-dimensions}
\end{table}

@@

\begin{table}[htb]
  \centering
  \caption{$k_\text{eff}$ values from \gls{MSRE} experimental data, the \gls{MSRE} numerical
  benchmark \cite{fratoni_molten_2020}, and the OpenMC and Moltres models in this work.}
  \begin{tabular}{l S[table-format=1.5(2)]}
    \toprule
     & {$k_\text{eff}$} \\
     \cmidrule(l){2-2}
    \gls{MSRE} experimental data & 1.00000(420) \\
    Serpent 2 (Numerical benchmark) & 1.02132(3) \\
    OpenMC (This work) & 1.01308(20) \\
    Hybrid (This work) & 1.01955 \\
    Diffusion (This work) & 1.01885 \\
    \bottomrule
  \end{tabular}
  \label{table:initial-crit}
\end{table}

@@

Every 3-D hybrid method $k$-eigenvalue
simulation of the \gls{MSRE} consisted of 747,688,760 \glspl{DOF} and 1,690,777,728 \glspl{DOF} for
the neutron diffusion and $S_N$ components, respectively. Each \gls{DOF} corresponds to a scalar
or angular group flux variable value defined at a mesh node. Each simulation ran with the distributed
mesh feature, which partitions and distributes the mesh across however many \gls{MPI} ranks used
in the simulation. All variable and mesh-linked data are also distributed with the mesh. This
greatly reduces memory requirements compared to storing the full mesh for each \gls{MPI} rank.

Each 3-D \gls{MSRE} simulation required at least forty nodes for sufficient memory to run. This
sets a strict minimum requirement for the 3-D hybrid simulations. On forty nodes, the simulations
required approximately 2.2 h to complete for a total of 88 node-hours or 2816 core-hours. The
distributed mesh capability comes with the cost of increased data transfer times between the $S_N$
and diffusion solvers due to increased inter-core data transfers. Transfers accounted for
approximately 0.675 h or 30 \% of the total simulation time. Future research into optimizing mesh
distribution and transfer-related data caching may help to minimize data transfers and speed-up
hybrid method simulations. The solution time for the initial neutron diffusion calculation with zero
drift correction also takes up approximately 30 \% of the total simulation time. After subtracting
the minor computational cost of evaluating the drift term even if it is zero, the hybrid method
requires about four times the solution time of the standard neutron diffusion method.

@@

For 3-D simulations, the \gls{MSRE} experimental data and the \gls{MSRE} numerical benchmark
report \cite{fratoni_molten_2020} both served as references for model validation. The numerical
benchmark is included in the International Reactor Physics Experiment Evaluation Project (IRPhEP)
handbook. The
$k_\text{eff}$ estimates of the \gls{MSRE} at initial criticality from OpenMC, the hybrid method,
and the neutron diffusion method in this work showed good agreement with the \gls{MSRE} numerical
benchmark. All numerical $k_\text{eff}$ estimates, including that from the benchmark report
\cite{fratoni_molten_2020}, exceeded the \gls{MSRE} experimental value by 1-2 \% due to possible
biases and uncertainties in the neutronic properties of graphite. Temperature reactivity
coefficient values from OpenMC, the hybrid method, and the neutron diffusion method also show good
agreement with the \gls{MSRE} data within experimental uncertainty with percentage discrepancies of
about 3 \%, but differ from the numerical benchmark which has a percentage discrepancy of -6.7 \%.

>>>>

In Chapter \ref{chap:hybrid}, I laid out the mathematical background and numerical implementation
of the hybrid $S_N$-diffusion method for improving neutronic accuracy in reactor systems containing
highly neutron-absorbing regions. I developed and implemented the diffusion and drift correction
schemes for the hybrid method in Python and using Moltres, respectively. This chapter demonstrates
the hybrid method through 1-D, 2-D, and 3-D $k$-eigenvalue simulations of the \gls{MSRE}.
I employed the OpenMC Monte Carlo neutral particle transport software \cite{romano_openmc:_2015} to
generate group constants for the hybrid method and reference solutions for method verification.
The 1-D models serve to verify the newly-implemented $S_N$ and hybrid methods
against OpenMC as well as to analyze the impact of key input parameters on the hybrid method. The
2-D models test the hybrid method performance through increased spatial dimensionality and reduced
geometric asymmetry relative to the 1-D models. Lastly, the 3-D models serve as neutronics model
validation against the \gls{MSRE} benchmark model by Fratoni et al.\ \cite{fratoni_molten_2020}, a
testbed for \gls{HPC} scaling tests, and preparation for the time-dependent multiphysics
simulations in Chapter \ref{chap:transient}.

@@

Group constants relevant to the neutron diffusion, $S_N$ neutron transport, or both
methods are:
%
\begin{align*}
  \Sigma_{t,g}:& \mbox{ Macroscopic total cross section in group $g$,}
  \Sigma_{r,g}:& \mbox{ Macroscopic removal cross section in group $g$,}
  \Sigma_s^{g'\rightarrow g}:& \mbox{ Macroscopic group-to-group scattering cross section matrix,}
  \Sigma_{s,l}^{g'\rightarrow g}:& \mbox{ $l$-th Legendre moment of the macroscopic
  group-to-group scattering cross section matrix,}
  \Sigma_{sp,l}^{g'\rightarrow g}:& \mbox{ $l$-th Legendre moment of the macroscopic
  group-to-group scattering production cross section matrix,}
    D_g:& \mbox{ $P_1$-based diffusion coefficient in group $g$,}
  \nu\Sigma_{f,g}:& \mbox{ Product of the average number of neutrons produced per fission and the
  macroscopic fission cross section in group $g$,}
    \chi_g:& \mbox{ Neutron fission spectrum in group $g$.}
\end{align*}
%
I generated the group constants using OpenMC's multigroup cross section generation capability
\cite{boyd_multigroup_2019}. A group constant postprocessing script for Moltres
(\texttt{moltres\_xs.py}) parses OpenMC simulation output files and rewrites the group constant
data into a JSON format file suitable for Moltres simulations. While OpenMC provides most of the
group constants directly, the postprocessing script calculates $\Sigma_{r,g}$ as
%
\begin{align}
  \Sigma_{r,g} =& \sum^G_{g'\neq g}\Sigma_s^{g\rightarrow g'}+\Sigma_{a,g}-\left(\Sigma_{sp}^{g
    \rightarrow g} - \Sigma_s^{g\rightarrow g}\right)
  \shortintertext{where}
      \Sigma_{a,g} =& \mbox{ macroscopic absorption cross section in group $g$,} \nonumber \\
      \Sigma_{sp}^{g\rightarrow g} =& \mbox{ macroscopic scattering production cross section from
      group $g$ to $g$.} \nonumber
\end{align}
%
$\Sigma_{r,g}$ primarily represents the loss of neutrons from group $g$ through outscattering and
absorption. $\Sigma_{sp}^{g\rightarrow g}$ incorporates neutron multiplication effects from neutron
knockout reactions into the scattering cross section. Neutronics codes commonly identify neutron
knockout reactions as scattering reactions, but $\Sigma_{r,g}$ is a convenient parameter in which
to incorporate neutron knockout effects in the neutron diffusion method. I ran all test cases
for $S_N$ and hybrid method calculations with scattering cross sections approximated by up to 2nd
Legendre moments ($L=2$).

@@

The rest of this section pertains to the deterministic neutronics methods used in this work for
modeling the \gls{MSRE}.
For the 1-D models, I performed neutronics calculations with the $S_N$, neutron diffusion, and
hybrid method implementations on Moltres and Python. Table \ref{table:nts-methods} highlights the
differences between the two implementations. The $S_N$ neutron transport method implementation on
Moltres follows the methodology for solving the \gls{SAAF} formulation of the $S_N$ equations as
described in Section \ref{sec:saaf} while the implementation in Python follows the methodology
for solving the original first-order formulation as described in Section \ref{sec:python-sn}.

The implementations on Moltres discretize the problem domain in space using the finite element
method while the implementations in Python use finite difference or diamond difference schemes. The
most crucial difference lies in the transport correction formulations for the hybrid method. The
Moltres implementation uses the drift correction scheme described in Section
\ref{sec:drift-correction} while the Python implementation uses the diffusion correction
scheme described in Section \ref{sec:diffusion-correction}.

@@

This section presents the models, results, and discussion for the 1-D test cases.

@@

This section presents the models, results, and discussion of the 2-D cases.

@@

\begin{itemize}
  \item Neglected thermal expansion of all reactor components.
  \item Modeled the control rods as perfectly annular cylinders instead of beaded control elements
    strung on flexible steel cables. Neglected the inconel shells encasing the control elements and
    the steel helical cables linking the control elements together.
  \item Set channel pitch, width, and length to 2, 0.2, and 1.2 inches, respectively.
  \item Homogenized the INOR-8, graphite, and molten salt regions in the sample basket.
  \item Modified the outer edge of the core graphite to be circular with no jagged edges.
  \item Replaced partial channels with full-size channels near the edge of the core graphite.
  \item Ignored the thermal insulation and shield structures outside the core.
\end{itemize}

@@

This subsection presents the results and discussion of the 2-D quarter-core and full-core models.

@@

This section presents the models, results, and discussion of the 3-D \gls{MSRE} simulations.

@@

\begin{table}[htb]
  \centering
  \caption{List of reactor dimensions.}
  \begin{tabular}{l S}
    \toprule
    Reactor Specifications & {Value} \\
    \midrule
    Height [m] & 2.15 \\
    Radius [m] & 0.762 \\
    Vessel thickness [m] & 0.0254 \\
    Fuel channel length [m] & 0.03048 \\
    Fuel channel width [m] & 0.01016 \\
    Graphite lattice pitch [m] & 0.05080 \\
    \bottomrule
  \end{tabular}
  \label{table:reactor-dimensions}
\end{table}

@@

\begin{table}[htb]
  \centering
  \caption{$k_\text{eff}$ values from \gls{MSRE} experimental data, the \gls{MSRE} numerical
  benchmark \cite{fratoni_molten_2020}, and the OpenMC and Moltres models in this work.}
  \begin{tabular}{l S[table-format=1.5(2)]}
    \toprule
     & {$k_\text{eff}$} \\
     \midrule
    \gls{MSRE} experimental data & 1.00000(420) \\
    Serpent 2 (Numerical benchmark) & 1.02132(3) \\
    OpenMC (This work) & 1.01308(20) \\
    Hybrid (This work) & 1.01955 \\
    Diffusion (This work) & 1.01885 \\
    \bottomrule
  \end{tabular}
  \label{table:initial-crit}
\end{table}

@@

Every 3-D hybrid method $k$-eigenvalue
simulation of the \gls{MSRE} consisted of 747,688,760 \glspl{DOF} and 1,690,777,728 \glspl{DOF} for
the neutron diffusion and $S_N$ components, respectively. Each \gls{DOF} corresponds to a scalar
or angular group flux variable value defined at a mesh node. Each simulation ran with the distributed
mesh feature, which partitions and distributes the mesh across however many \gls{MPI} ranks used
in the simulation. All variable and mesh-linked data are also distributed with the mesh. This
greatly reduces memory requirements compared to storing the full mesh for each \gls{MPI} rank.
Each 3-D \gls{MSRE} simulation required at least forty nodes for sufficient memory to run. This
sets a strict minimum requirement for the 3-D hybrid simulations. A significant fraction of
memory use in Moltres comes from storing the residual and Jacobian quantities at each \gls{FEM}
quadrature point. Given that terms in the $S_N$ equations share the same Jacobian formulation
across all ordinate directions, memory use (and compute time) could be optimized by reducing
duplicate Jacobian evaluations.

On forty nodes, the simulations
required approximately 2.2 h to complete for a total of 88 node-hours or 2816 core-hours. The
distributed mesh capability comes with the cost of increased data transfer times between the $S_N$
and diffusion solvers due to increased inter-core data transfers. Transfers accounted for
approximately 0.675 h or 30 \% of the total simulation time. Future research into optimizing mesh
distribution and transfer-related data caching may help to minimize data transfers and speed up
hybrid method simulations. The solution time for the initial neutron diffusion calculation with zero
drift correction also takes up approximately 30 \% of the total simulation time. After subtracting
the minor computational cost of evaluating the drift term even if it is zero, the hybrid method
requires about four times the solution time of the standard neutron diffusion method.

@@

For 3-D simulations, the \gls{MSRE} experimental data and the \gls{MSRE} numerical benchmark
report \cite{fratoni_molten_2020} both served as references for model validation. The numerical
benchmark is included in the International Reactor Physics Experiment Evaluation Project (IRPhEP)
handbook. The
$k_\text{eff}$ estimates of the \gls{MSRE} at initial criticality from OpenMC, the hybrid method,
and the neutron diffusion method in this work showed good agreement with the \gls{MSRE} numerical
benchmark. All numerical $k_\text{eff}$ estimates, including that from the benchmark report
\cite{fratoni_molten_2020}, exceeded the \gls{MSRE} experimental value by 1-2 \% possibly due to
biases and uncertainties in the nuclear data library for graphite. Temperature reactivity
coefficient values from OpenMC, the hybrid method, and the neutron diffusion method also show good
agreement with the \gls{MSRE} data within experimental uncertainty with percentage discrepancies of
about 3 \%, but differ from the numerical benchmark which has a percentage discrepancy of -6.7 \%.
